---
title: "Indignificant notes"
output: html_document
date: "2022-10-14"
---

### Fynctions to list out insignificance between variables:
```{r}
raceList <- function(data){
  data %>%
    mutate(insigList = "",
           insigList = ifelse(sig_wht_blk == "no", "White and Black", insigList),
           insigList = ifelse(sig_wht_asian == "no", paste0(insigList,"White and Asian", sep = ", "), insigList),
           insigList = ifelse(sig_wht_hisp == "no", paste0(insigList,"White and Hispanic",sep = ", "), insigList),
           insigList = ifelse(sig_blk_hisp == "no", paste0(insigList,"Black and Hispanic",sep = ", "), insigList),
           insigList = ifelse(sig_blk_asian  == "no", paste0(insigList, "Black and Asian", sep = ", "), insigList),
           insigList = ifelse(sig_hisp_asian == "no", paste0(insigList, "Hispanic and Asian", sep = ", "), insigList),
           insigList = str_sub(insigList,1,-3)) %>%
  mutate(placename = ifelse(placename %in% c("Orleans", "Jefferson", "St. Tammany"), paste0(placename, " Parish"), placename)) %>%
  filter(insigList != "") %>%
  mutate(note = paste0("&#8224; : In ", placename, ", the difference between ", insigList, " is not statistically significant.")) %>%
  select(placename,note) %>%
  pivot_wider(names_from = "placename", values_from = "note") %>%
  unite("note", 1:dim(.)[2]) %>%
    as.data.frame()
}
```
```{r}
timeList <- function(data, compYear = 2000){
  if(compYear == 2000){
  data %>%
    mutate(insigList = "",
           insigList = ifelse(sig_00_10 == "no", paste0(insigList, " for 2000-2010", sep = ", "), insigList),
           insigList = ifelse(sig_00_21 == "no", paste0(insigList, " for 2000-2021", sep = ", "), insigList),
           insigList = ifelse(sig_10_21 == "no", paste0(insigList, " for 2010-2021", sep = ", "), insigList),
           insigList = str_sub(insigList,1,-3)) %>%
  filter(insigList != "") %>%
  mutate(note = paste0("&#8224; = Change in time is not significant for ", race, insigList, ".")) %>%
  select(race,note) %>%
  pivot_wider(names_from = "race", values_from = "note") %>%
  unite("note", 1:dim(.)[2]) %>%
    as.data.frame()
  } else{
    data %>%
    mutate(insigList = "",
           insigList = ifelse(sig_99_10 == "no", paste0(insigList, " for 1999-2010", sep = ", "), insigList),
           insigList = ifelse(sig_99_21 == "no", paste0(insigList, " for 1999-2021", sep = ", "), insigList),
           insigList = ifelse(sig_10_21 == "no", paste0(insigList, " for 2010-2021", sep = ", "), insigList),
           insigList = str_sub(insigList,1,-3)) %>%
  filter(insigList != "") %>%
  mutate(note = paste0("&#8224; = Change in time is not significant for ", race, insigList, ".")) %>%
  select(race,note) %>%
  pivot_wider(names_from = "race", values_from = "note") %>%
  unite("note", 1:dim(.)[2]) %>%
    as.data.frame()
  }
}
```

### Bachelor/educational attainment ###
```{r}
bachracelist <- raceList(bach.race_stattest)
print(bachracelist$note)
```

&#8224; : In Orleans Parish, the difference between Hispanic and Asian is not statistically significant.
&#8224; : In Jefferson Parish, the difference between White and Asian and Black and Hispanic is not statistically significant.
&#8224; : In St. Tammany Parish, the difference between Black and Hispanic, Black and Asian, and Hispanic and Asian is not statistically significant.

```{r}

bachtimelist <- timeList(bach.hist_stattest)
print(bachtimelist$note)

```
&#8224; : Change in time is not significant for Hispanic for 2000-2010.


### Median household income ###
```{r}
medhhracelist <- raceList(medhh.race_stattest)
print(medhhracelist$note)
```

&#8224; = In Orleans Parish, the difference between White and Asian is not statistically significant.
&#8224; = In Jefferson Parish, the difference between White and Asian, White and Hispanic, and Hispanic and Asian is not statistically significant.
&#8224; = In St. Tammany Parish, the difference between White and Asian, White and Hispanic, Black and Hispanic, Black and Asian, and Hispanic and Asian is not statistically significant.
&#8224; = In the New Orleans Metro Area, the difference between White and Asian and Hispanic and Asian is not statistically significant.

```{r}

medhhtimelist <- timeList(medhh.hist_stattest, compYear = 1999)
print(medhhtimelist$note)

```
&#8224; : Change in time is not significant for Black for 2010-2021.
&#8224; : Change in time is not significant for any race for 1999-2010.

### Poverty ###
```{r}
povracelist <- raceList(pov.race_stattest)
print(povracelist$note)
```
&#8224; = In Orleans Parish, the difference between White and Asian and Hispanic and Asian is not statistically significant.
&#8224; = In Jefferson Parish, the difference between White and Hispanic, Black and Asian, and Hispanic and Asian is not statistically significant.
&#8224; = In New Orleans Metro Area, the difference between Hispanic and Asian is not statistically significant.
```{r}
povtimelist <- timeList(pov.hist_stattest)
print(povtimelist$note)

```
&#8224; = Change in time is not significant for any race for 2000-2021 or 2010-2021.
&#8224; = Change in time is not significant for Black and Hispanic, any race for 2000-2010.


### Child poverty ###
```{r}
childpovracelist <- raceList(childpov.race_stattest)
print(childpovracelist$note)
```
&#8224; = In Orleans Parish, the difference between White and Asian and Hispanic and Asian is not statistically significant.
&#8224; = In Jefferson Parish, the difference between White and Asian, Black and Asian, and Hispanic and Asian is not statistically significant.
&#8224; = In the New Orleans Metro Area, the difference between White and Asian and Hispanic and Asian is not statistically significant.
&#8224; = In United States, the difference between White and Asian is not statistically significant.
```{r}

childpovtimelist <- timeList(childpov.hist_stattest)
print(childpovtimelist$note)

```
&#8224; = Change in time is not significant for any race for 2000-2021 or 2010-2021.
&#8224; = Change in time is not significant for White, non-Hispanic for 2000-2010.

### Homeownership ###
```{r}
horacelist <- raceList(ho.race_stattest)
print(horacelist$note)
```
&#8224; = In Orleans Parish, the difference between White and Asian, Black and Hispanic, and Black and Asian is not statistically significant.
&#8224; = In Jefferson Parish, the difference between White and Asian is not statistically significant.
&#8224; = In St. Tammany Parish, the difference between White and Asian, White and Hispanic, Black and Hispanic, Black and Asian, and Hispanic and Asian is not statistically significant.
```{r}

hotimelist <- timeList(ho.hist_stattest %>% mutate(sig_00_10 = ""))
print(hotimelist$note)

```
&#8224; = Change in time is not significant for Black for 2010-2021.
&#8224; = Change in time is not significant for Hispanic,any race for 2000-2021.



